---
title: "Project week 14- part 3"
output: html_document
---

## 1. Define the Question

This is will help us understand the task at hand, the dataset to be used and the metrics of Success.

### a. Specifying the question.
  Our project has been divided into four parts where we will explore a recent marketing dataset by performing various unsupervised learning techniques and later providing recommendations based on our insights. 
 
### b. Define the Metrics of Success.
Our metrics of success is to be able to do a conclusive Dimensionality reduction(Anomaly Detection) through the various methods.

### c. Understand context
The context is using data to do dimensionality reduction through Anomaly Detection and other ways to get meaningful insights and conclusions from advertising data.

### d. Record the experiment design 
This involves:
a. Cleaning
   i). Removing anomalies in the data
  ii). Finding and dealing with missing data
 iii). Dealing with duplicated rows in the data
 
b. Exploratory Data Analysis
   i). Univariate analysis
  ii). Bivariate analysis
 iii). Multivariate analysis 
 
c. Anomaly detection
  
### e. Data relevance
To establish if the data is relevant to the question and the objectives of the experiment.

## Checking our data

```{r}
## Loading our libraries

library(readr)
```

```{r}
## Importing our data

forecast <- read_csv("C:/Users/HP/Downloads/Supermarket_Sales_Forecasting - Sales.csv")


```

## 2. Read Data

```{r}
## Previewing the top of our dataset

head(forecast)
```

```{r}
## previewing the bottom of our data

tail(forecast)

```
```{r}
## Determining the shape of our data
dim(forecast)

```

```{r}
## Determining the summary of the data

summary(forecast)
```

```{r}
## Checking the column names

colnames(forecast)


```
```{r}
## Checking the class of our data

class(forecast)

```

```{r}
## Checking the structure of our data

str(forecast)
```
## Tidying our data
```{r}
## Checking for null values

colSums(is.na(forecast))  

```
```{r}
## Checking for duplicate values

Duplicate <- forecast[duplicated(forecast),]
Duplicate

```

```{r}
## Checking for outliers in our data

boxplot(forecast$Sales)
```
```{r}
boxplot(forecast$Sales)$out
```



```{r}
## Loading the normalize and tidyverse libraries

library(tidyverse)
library(anomalize)

```





```{r}
## Using the anomalize library to check for anomalies in our data

tidyverse_cran_downloads %>%
    time_decompose(count) %>%
    anomalize(remainder) %>%
    time_recompose() %>%
    plot_anomalies(time_recomposed = TRUE, ncol = 3, alpha_dots = 0.5)


```

